The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-29 article.tex
Typo fix.

Prior to CDK \cdkversion{}, the parity of the version identifier's second digit 
indicated stability. Even numbers (v1.2.x, v1.4.x) indicating API stability and
odd numbers (v1.3.x, v1.5.x) indicating potential API instability. Versions 
v1.4.x and v1.5.x were developed in parallel, where possible patches were
applied to both. As the APIs diverged the amount of effort to port patches
from the development but more robust v1.5.x to v1.4.x 
became unmanageable for the core development team. This even-odd version scheme
was adopted from old Linux kernal versioning that was subsequently
abandoned in 2004 for time-based releases~\cite{LinuxKernalVersionNumbering}.

>>>>

Prior to CDK \cdkversion{}, the parity of the version identifier's second digit 
indicated stability. Even numbers (v1.2.x, v1.4.x) indicating API stability and
odd numbers (v1.3.x, v1.5.x) indicating potential API instability. Versions 
v1.4.x and v1.5.x were developed in parallel, where possible patches were
applied to both. As the APIs diverged the amount of effort to port patches
from the development but more robust v1.5.x to v1.4.x 
became unmanageable for the core development team. This even-odd version scheme
was adopted from old Linux kernel versioning that was subsequently
abandoned in 2004 for time-based releases~\cite{LinuxKernalVersionNumbering}.
